\bibitem[*]{cmsphyspapers}
        {\bf CMS physics papers}
        \\    

\bibitem[pub38]{monojet} 
  A.~M.~Sirunyan {\it et al.} [CMS Collaboration],
  ``Search for dark matter produced with an energetic jet or a hadronically decaying W or Z boson at $ \sqrt{s}=13 $ TeV,''
  JHEP {\bf 1707}, 014 (2017)

\bibitem[pub37]{photonpaper} 
  V.~Khachatryan {\it et al.} [CMS Collaboration],
  ``Performance of Photon Reconstruction and Identification with the CMS Detector in Proton-Proton Collisions at sqrt(s) = 8 TeV,''
  JINST {\bf 10}, no. 08, P08010 (2015)

\bibitem[pub36]{elepaper} 
  V.~Khachatryan {\it et al.} [CMS Collaboration],
  ``Performance of Electron Reconstruction and Selection with the CMS Detector in Proton-Proton Collisions at $\sqrt{s}$ = 8  TeV,''
  JINST {\bf 10}, no. 06, P06005 (2015)

\bibitem[pub35]{h4l_jcp} 
  V.~Khachatryan {\it et al.} [CMS Collaboration],
  ``Constraints on the spin-parity and anomalous HVV couplings of the Higgs boson in proton collisions at 7 and 8 TeV,''
  Phys.\ Rev.\ D {\bf 92}, no. 1, 012004 (2015)

\bibitem[pub34]{h4l_legacy} 
  S.~Chatrchyan {\it et al.} [CMS Collaboration],
  ``Measurement of the properties of a Higgs boson in the four-lepton final state,''
  Phys.\ Rev.\ D {\bf 89}, no. 9, 092007 (2014)

\bibitem[33]{h4l_differential} 
  V.~Khachatryan {\it et al.} [CMS Collaboration],
  ``Measurement of differential and integrated fiducial cross sections for Higgs boson production in the four-lepton decay channel in pp collisions at $ \sqrt{s}=7 $ and 8 TeV,''
  JHEP {\bf 1604}, 005 (2016)

\bibitem[pub32]{Chatrchyan:2013iaa} 
  S.~Chatrchyan {\it et al.} [CMS Collaboration],
  ``Measurement of Higgs boson production and properties in the WW decay channel with leptonic final states,''
  JHEP {\bf 1401}, 096 (2014)

\bibitem[pub31]{higgsprop}
  S.~Chatrchyan {\it et al.}  [CMS Collaboration],
  ``Study of the Mass and Spin-Parity of the Higgs Boson Candidate via Its Decays to Z Boson Pairs'',
  Phys.\ Rev.\ Lett.\  {\bf 110}, 081803 (2013)

\bibitem[pub30]{higgsdiscovery} 
  S.~Chatrchyan {\it et al.}  [CMS Collaboration],
  ``Observation of a new boson at a mass of 125 GeV with the CMS experiment at the LHC,''
  Phys.\ Lett.\ B {\bf 716}, 30 (2012)

\bibitem[pub29]{Chatrchyan:2012ty} 
  S.~Chatrchyan {\it et al.}  [CMS Collaboration],
  ``Search for the standard model Higgs boson decaying to a W pair in the fully leptonic final state in pp collisions at sqrt(s) = 7 TeV,''
  Phys.\ Lett.\ B {\bf 710}, 91 (2012)

\bibitem[pub28]{Chatrchyan:2012tx} 
  S.~Chatrchyan {\it et al.}  [CMS Collaboration],
  ``Combined results of searches for the standard model Higgs boson in pp collisions at sqrt(s) = 7 TeV,''
  Phys.\ Lett.\ B {\bf 710}, 26 (2012)

\bibitem[pub27]{Chatrchyan:2012dg} 
  S.~Chatrchyan {\it et al.}  [CMS Collaboration],
  ``Search for the standard model Higgs boson in the decay channel H to ZZ to 4 leptons in pp collisions at sqrt(s) = 7 TeV,''
  Phys.\ Rev.\ Lett.\  {\bf 108}, 111804 (2012)

\bibitem[pub26]{Chatrchyan:2011jz} 
  S.~Chatrchyan {\it et al.} [CMS Collaboration],
  ``Measurement of the lepton charge asymmetry in inclusive $W$ production in pp collisions at $\sqrt{s}$ = 7 TeV,''
  JHEP {\bf 1104}, 050 (2011)

\bibitem[pub25]{cms_hww_paper2010}
  CMS~Collaboration,
  ``Measurement of $W^+W^-$ production and search for the Higgs boson in pp collisions at $\sqrt{s}$ = 7 TeV''
  Physics Letters B {\bf 699}, 25 (2010)

\bibitem[pub24]{Chatrchyan:2011ek} 
  S.~Chatrchyan {\it et al.}  [CMS Collaboration],
  ``Inclusive search for squarks and gluinos in $pp$ collisions at $\sqrt{s}=7$ TeV,''
  Phys.\ Rev.\ D {\bf 85}, 012004 (2012)

\bibitem[pub23]{cms_vecbos_paper}
  CMS~Collaboration,
  ``Jet Production Rates in Association with W and Z Bosons in pp Collisions at sqrt(s) = 7 TeV''
  JHEP {\bf 1201}, 010 (2012)

\bibitem[pub22]{Khachatryan:2010xn} 
  V.~Khachatryan {\it et al.}  [CMS Collaboration],
  ``Measurements of Inclusive W and Z Cross Sections in pp Collisions at sqrt(s)=7 TeV,''
  JHEP {\bf 1101}, 080 (2011)

\bibitem[pub21]{inclusiveV_2010} 
  S.~Chatrchyan {\it et al.} [CMS Collaboration],
  ``Measurement of the Inclusive $W$ and $Z$ Production Cross Sections in $pp$ Collisions at $\sqrt{s}=7$ TeV,''
  JHEP {\bf 1110}, 132 (2011)


\vskip 1.0 truecm

\bibitem[*]{cmsdetpapers}
{\bf CMS detector papers}
\\

\bibitem[pub20]{cms_craft}
  CMS~Collaboration,
  ``Commissioning of the CMS experiment and the cosmic run at four tesla'',
  JINST {\bf 5} (2010) T03001

\bibitem[pub19]{ecal_craft}
 CMS~Collaboration
 ``Performance and operation of the CMS electromagnetic calorimeter''
 JINST {\bf 5} (2010) T03010

\bibitem[pub18]{time_craft}
 CMS~Collaboration
 `` Time reconstruction and performance of the CMS electromagnetic calorimeter''
 JINST {\bf 5} (2010) T03011

%\cite{:2008zzk}
\bibitem[pub17]{longo_cms}
  R.~Adolphi {\it et al.}  [CMS Collaboration],
  ``The CMS experiment at the CERN LHC,''
  JINST {\bf 3} (2008) S08004





\vskip 1.0 truecm

\bibitem[*]{babarphyspapers}
{\bf BaBar physics papers}

%\cite{Aubert:2008gy}
\bibitem[pub16]{Aubert:2008gy}
  B.~Aubert {\it et al.}  [BABAR Collaboration],
  ``Measurement of Time-Dependent CP Asymmetry in $B^0 \to K^0_{S} \pi^0
  \gamma$ Decays,''
  Phys.\ Rev.\  D {\bf 78} (2008) 071102
  %%CITATION = PHRVA,D78,071102;%%


%\cite{Aubert:2007sd}
\bibitem[pub15]{Aubert:2007sd}
  B.~Aubert {\it et al.}  [BABAR Collaboration],
  ``Measurements of CP-Violating Asymmetries in the Decay $B^0 \to K^+K^-K^0$''
  Phys.\ Rev.\ Lett.\  {\bf 99}, 161802 (2007)
%  [arXiv:0706.3885 [hep-ex]].
  %%CITATION = PRLTA,99,161802;%%

%\cite{Aubert:2007me}
\bibitem[pub14]{Aubert:2007me}
  B.~Aubert {\it et al.}  [BABAR Collaboration],
  ``Measurement of CP Asymmetries in $B^0 \to K^0_S K^0_S K^0_S$ Decays'',
  Phys.\ Rev.\  D {\bf 76}, 091101 (2007)
%  [arXiv:hep-ex/0702046].
  %%CITATION = PHRVA,D76,091101;%%

%\cite{Aubert:2007mj}
\bibitem[pub13]{Aubert:2007mj}
  B.~Aubert {\it et al.}  [BABAR Collaboration],
  ``Observation of CP violation in $B^0 \to K^{+} \pi^{-}$ and $B^0 \to \pi^{+} \pi^{-}$,''
  Phys.\ Rev.\ Lett.\  {\bf 99}, 021603 (2007)
%  [arXiv:hep-ex/0703016].
  %%CITATION = PRLTA,99,021603;%%

%\cite{Aubert:2007mgb}
\bibitem[pub12]{Aubert:2007mgb}
  B.~Aubert {\it et al.}  [BABAR Collaboration],
  ``Measurement of the CP-violating asymmetries in $B^0 \to K^0_{S} \pi^0$ and of the branching fraction of $B^0 \to K^0 \pi^0$,''
  Phys.\ Rev.\  D {\bf 77}, 012003 (2008)
  %%[arXiv:0707.2980 [hep-ex]].
  %%CITATION = PHRVA,D77,012003;%%

\bibitem[pub11]{Aubert:2007hm} 
  B.~Aubert et al. [BABAR Collaboration] 
  {\it ``Improved measurement of CP violation in neutral B decays to $c \bar{c} s$''},
  Phys.\ Rev.\ Lett.\  {\bf 99}, 171803 (2007)
 % Arxiv:hep-ex/0703021.

%\cite{Aubert:2006nn}
\bibitem[pub10]{Aubert:2006nn}
  B.~Aubert {\it et al.}  [BABAR Collaboration],
  ``Search for $B^+ \to \phi \pi^+$ and $B^0 \to \phi \pi^0$ decays,''
  Phys.\ Rev.\ D {\bf 74}, 011102 (2006)
%  [arXiv:hep-ex/0605037].
  %%CITATION = HEP-EX 0605037;%%

%\cite{Aubert:2006nu}
\bibitem[pub9]{Aubert:2006nu}
  B.~Aubert {\it et al.}  [BABAR Collaboration],
  ``Dalitz plot analysis of the decay $B^{\pm} \to K^{\pm} K^{\pm} K^{\mp}$,''
  Phys.\ Rev.\  D {\bf 74}, 032003 (2006)
%  [arXiv:hep-ex/0605003].
  %%CITATION = PHRVA,D74,032003;%%


%\cite{Aubert:2006wv}
\bibitem[pub8]{Aubert:2006wv}
  B.~Aubert {\it et al.}  [BABAR Collaboration],
  ``Observation of CP violation in $B^0 \to \eta^\prime K^0$ decays,''
  Phys.\ Rev.\ Lett.\  {\bf 98}, 031801 (2007)
  %%[arXiv:hep-ex/0609052].
  %%CITATION = PRLTA,98,031801;%%

%\cite{Aubert:2006zy}
\bibitem[pub7]{Aubert:2006zy}
  B.~Aubert {\it et al.}  [BABAR Collaboration],
  ``Search for the decay $B^0 \to K^0_{s} K^0_{s} K^0_{L}$,''
  Phys.\ Rev.\  D {\bf 74}, 032005 (2006)
  %%[arXiv:hep-ex/0606031].
  %%CITATION = PHRVA,D74,032005;%%

%\cite{Aubert:2006gm}
\bibitem[pub6]{Aubert:2006gm}
  B.~Aubert {\it et al.}  [BABAR Collaboration],
  ``Observation of $B^{+} \to \bar{K}^0 K^{+}$ and $B^0 \to K^0 \bar{K}^0$,''
  Phys.\ Rev.\ Lett.\  {\bf 97}, 171805 (2006)
  %%[arXiv:hep-ex/0608036].
  %%CITATION = PRLTA,97,171805;%%

%\cite{Aubert:2005ja}
\bibitem[pub5]{Aubert:2005ja}
  B.~Aubert {\it et al.}  [BABAR Collaboration],
   ``Measurement of CP asymmetries in $B^0 \to \phi K^0$ and $B^0 \to K^+ K^-K^0_S$  decays,''
  Phys.\ Rev.\ D {\bf 71}, 091102 (2005)
%  [arXiv:hep-ex/0502019].
  %%CITATION = HEP-EX 0502019;%%

%\cite{Aubert:2005dy}
\bibitem[pub4]{Aubert:2005dy}
  B.~Aubert {\it et al.}  [BABAR Collaboration],
  ``Branching fraction and CP asymmetries of $B^0 \to K^0_S K^0_S K^0_S$'', 
  Phys.\ Rev.\ Lett.\  {\bf 95}, 011801 (2005)
%  [arXiv:hep-ex/0502013].
  %%CITATION = HEP-EX 0502013;%%


\vskip 1.0 truecm

\bibitem[*]{babardetpapers}
{\bf BaBar detector papers}

%\cite{Anulli:2005wi}
\bibitem[pub3]{Anulli:2005wi}
  F.~Anulli {\it et al.},
  ``Performance of 2nd generation BaBar resistive plate chambers,''
  Nucl.\ Instrum.\ Meth.\ A {\bf 552}, 276 (2005)

%\cite{Band:2008zzb}
\bibitem[pub2]{Band:2008zzb}
  H.~R.~Band {\it et al.},
  ``Study Of HF Production In BaBar Resistive Plate Chambers'',
  Nucl.\ Instrum.\ Meth.\  A {\bf 594}, 33 (2008).

\bibitem[pub1]{BandProc}
  H.~R.~Band {\it et al.},
  ``Performance and Aging Studies of BaBar Resistive Plate Chambers''
  Nucl.\ Physics B {\bf 158}, 139-142 (2006).

\vskip 1.0 truecm

\bibitem[*]{otherpapers}
{\bf Other papers}

\bibitem[opub2]{pinci_jinst}
  C.~Antochi~Vasile {\it et al.},
  ``Combined readout of a triple-GEM detector''
  Submitted to JINST (2018)

\bibitem[opub1]{h4l_8d}
  Y.~Chen, E.~Di Marco, J.~Lykken, M.~Spiropulu, R.~Vega-Morales and S.~Xie,
  ``8D likelihood effective Higgs couplings extraction framework in $h \to 4\ell$,''
  JHEP {\bf 1501}, 125 (2015)

